Supplemental information

### 2017-09-20 manuscript/supplemental.tex
partly formatted R code for nice compiling

@@

@@

@@

@@

  \vspace{12pt}
  calculate\_parameters\textless-function(priordata,n,k)\{
  \# Calculate the parameters of the prior distribution
  pars=fitdistr(x=priordata,"beta",start=list(shape1=1,shape2=1),lower=c(0,0))\$estimate
  alpha=pars[[1]]
  beta=pars[[2]]
  \# Update the parameters with data. If n=0 and k=0, no change.
  alpha\_prime=alpha+k
  beta\_prime=beta+n-k
  pars2=c(alpha\_prime,beta\_prime)
  return(pars2)
  }

    % calculate_parameters<-function(priordata,n,k){
    %   pars=fitdistr(x=priordata,"beta",start=list(shape1=1,shape2=1),lower=c(0,0))$estimate
    %   alpha=pars[[1]]
    %   beta=pars[[2]]
    %   alpha_prime=alpha+k
    %   beta_prime=beta+n-k
    %   pars2=c(alpha_prime,beta_prime)
    %   return(pars2)
    % }

@@

    \vspace{12pt}
    calculate\_distribution\textless-function(pars){
      \# alpha and beta may be from a prior or posterior distribution
      alpha=pars[[1]]
      beta=pars[[2]]

      \# Calculate the MLE of the mean
      mu\_num=alpha
      mu\_den=alpha+beta
      mu=mu\_num\/mu\_den

      \# Calculate the MLE of the variance
      sig\_num=alpha\*beta
      den1=alpha+beta
      den2=den1\*\*2
      sig\_den=den1\*den2
      sigma2=sig\_num\/sig\_den

      return(c(mu,sigma2))
    }

  % calculate_distribution<-function(pars){
  %       alpha=pars[[1]]
  %       beta=pars[[2]]

  %       mu_num=alpha
  %       mu_den=alpha+beta
  %       mu=mu_num/mu_den

  %       sig_num=alpha*beta
  %       den1=alpha+beta
  %       den2=den1**2
  %       sig_den=den1*den2
  %       sigma2=sig_num/sig_den

  %       return(c(mu,sigma2))
  %     }

@@

  \vspace{12pt}

credible_interval<-function(pars,p_lower,p_upper){
  alpha=pars[[1]]
  beta=pars[[2]]
  lowCI=qbeta(p=p_lower,shape1=alpha,shape2=beta)
  highCI=qbeta(p=p_upper,shape1=alpha,shape2=beta)
  return(c(lowCI,highCI))
}

plot_precision<-function(threshold,confidence,pars){
  alpha=pars[[1]]
  beta=pars[[2]]
  n=seq(0,100,1)
  k=0
  cdf=pbeta(threshold,shape1=alpha,shape2=beta+n)
  samples=length(which(cdf<confidence))
  # plot(n,cdf,type="l",xlab="n",ylab="Cumulative distribution")
  # abline(h=0.95,lty=3)
  return(samples)
}

>>>>

\documentclass[12pt]{article} 
\usepackage{amsmath} 
\usepackage[dvips]{graphicx}
\usepackage{multirow} 
\usepackage{geometry} 
\usepackage{pdflscape}
\usepackage[labelfont=bf]{caption} 
\usepackage{setspace}
\usepackage[running]{lineno} 
% \usepackage[numbers,sort]{natbib}
\usepackage[round]{natbib} 
\usepackage{array}

\newcommand{\methods}{\textit{Materials \& Methods}}
\newcommand{\SI}{\textit{Appendix}~}

\topmargin -1.5cm % 0.0cm 
\oddsidemargin 0.0cm % 0.2cm 
\textwidth 6.5in
\textheight 9.0in % 21cm
\footskip 1.0cm % 1.0cm

\usepackage{authblk}

\title{Supplemental information}

\author{Authors}
\date{\small$^1$Department of Physics, Chemistry\\ 
and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
% \medskip
% $^\dagger$ Corresponding author:\\
% alyssa.cirtwill@gmail.com\\
% +46 723 158464\\
 }

\renewcommand\Authands{ and }

\begin{document} 
\maketitle 
\raggedright
\setlength{\parindent}{15pt} 
\clearpage

@@

      \vspace{12pt}
      \emph{
      \noindent \hspace{-4pt} prior\_web\_data=read.csv(``tree\_level\_interaxn\_all\_plants\_traits\_size.csv")\\
      \# Remove extra data on parasitoids, etc.\\
      prior\_web\_data[,31:57]\textless-NULL\\
      prior\_web\_data[,4:26]\textless-NULL\\
      prior\_web\_data[,2]\textless-NULL\\
      \# Build a web with interactions=1 for any galler observed on any genotype\\
      prior\_web=matrix(nrow=26,ncol=4)\\
      for(r in 1:length(levels(prior\_web\_data\$Genotype)))\{\\
      \hspace{4pt}  gen=levels(prior\_web\_data\$Genotype)[r]\\
      \hspace{4pt}  subset=prior\_web\_data[which(prior\_web\_data\$Genotype==gen),]\\
      \hspace{4pt}  for(c in 1:4)\{\\
      \hspace{8pt}    if(sum(subset[,2+c])\textgreater0)\{\\
      \hspace{12pt}      prior\_web[r,c]=1\\
      \hspace{8pt}    \} else \{\\
      \hspace{12pt}      prior\_web[r,c]=0\\
      \hspace{8pt}    \}\}\}
      }

@@

      \vspace{12pt}
      \emph{
      \noindent \hspace{-4pt} \# Now get the degree distributions from the web\\
      deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
      \# Remove one genotype that never interacted\\
      deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
      deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
      \# Interaction probabilities are the product of plant and galler probabilities\\
      int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
      }

@@

\clearpage

@@

  \vspace{12pt}
  \emph{
  \noindent \hspace{-4pt}calculate\_parameters\textless-function(priordata,n,k)\{\\
  \hspace{4pt} \# Calculate prior parameters\\
  \hspace{4pt} start=list(shape1=1,shape2=1)
  \hspace{80pt} pars=fitdistr(x=priordata,`beta',start=start,lower=c(0,0))\$estimate\\
  \hspace{4pt} alpha=pars[[1]]\\
  \hspace{4pt} beta=pars[[2]]\\
  \hspace{4pt} \# Update the parameters with data. If n=0 and k=0, no change.\\
  \hspace{4pt} alpha\_prime=alpha+k\\
  \hspace{4pt} beta\_prime=beta+n-k\\
  \hspace{4pt} pars2=c(alpha\_prime,beta\_prime)\\
  \hspace{4pt} return(pars2) \}
  }
  \vspace{12pt}

@@

    \vspace{12pt}
    \emph{
    calculate\_distribution\textless-function(pars)\{\\
      \# alpha and beta may be from a prior or posterior distribution\\
      alpha=pars[[1]]\\
      beta=pars[[2]]\\

      \# Calculate the MLE of the mean\\
      mu\_num=alpha\\
      mu\_den=alpha+beta\\
      mu=mu\_num\/mu\_den\\

      \# Calculate the MLE of the variance\\
      sig\_num=alpha\*beta\\
      den1=alpha+beta\\
      den2=den1\*\*2\\
      sig\_den=den1\*den2\\
      sigma2=sig\_num\/sig\_den\\

      return(c(mu,sigma2))\}
    }
  \vspace{12pt}

@@

  \vspace{12pt}
  \emph{
  credible\_interval\textless-function(pars,p\_lower,p\_upper)\{\\
    alpha=pars[[1]]\\
    beta=pars[[2]]\\
    lowCI=qbeta(p=p\_lower,shape1=alpha,shape2=beta)\\
    highCI=qbeta(p=p\_upper,shape1=alpha,shape2=beta)\\
    return(c(lowCI,highCI))\}
  }

  \vspace{12pt}
  \emph{
  plot\_precision\textless-function(threshold,confidence,pars)\{\\
    alpha=pars[[1]]\\
    beta=pars[[2]]\\
    n=seq(0,100,1)\\
    k=0\\
    cdf=pbeta(threshold,shape1=alpha,shape2=beta+n)\\
    samples=length(which(cdf<confidence))\\
    return(samples) \}
  }

\clearpage

    \bibliographystyle{ecollett} 
    \bibliography{manual_abbrev} % Abbreviate journal titles.

\end{document}
